---
title: "Training and Test dataset of DeePlexiCon and Poreplex"
author: "Chao Tang"
date: 'Report created: `r Sys.Date()`'
output: 
  html_document: 
    code_folding: "hide"
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: false
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval      = T, #在块中运行代码(default = TRUE)
                      highlight = T, #高亮显示
                      echo      = F, #是否在输出中包含源代码
                      tidy      = T, #是否整理代码
                      error     = T, #是否在输出中包含错误信息
                      warning   = F, #是否在输出中包含警告(default = TRUE)
                      message   = F, #是否在输出中包含参考的信息
                      cache.    = F)
knitr::opts_knit$set(root.dir = "/mnt/raid61/Personal_data/tangchao/40TCellsQTL4")
```

```{r}
library(data.table)
library(ggplot2)
library(ggpubr)
library(parallel)
library(ggridges)
```

# Reads of Poreplex & DeePlexiCon barcodes

```{r}
read2gene_20200605 <- fread("/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/02.BamReadsSplit/read2gene_20200605.txt")
read2gene_20200620 <- fread("/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/02.BamReadsSplit/read2gene_20200620.txt")
read2gene_20200902 <- fread("/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/02.BamReadsSplit/read2gene_20200902.txt")
read2gene_20201127 <- fread("/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/02.BamReadsSplit/read2gene_20201127.txt")
```

```{r}
read2gene_20200605[, read := paste0("read_", read)]
read2gene_20200620[, read := paste0("read_", read)]
read2gene_20200902[, read := paste0("read_", read)]
read2gene_20201127[, read := paste0("read_", read)]
```

```{r}
read2gene_20200902 <- read2gene_20200902[grepl("^[DP]-", Name), ]
read2gene_20201127 <- read2gene_20201127[grepl("^[DP]-", Name), ]
```

# Signal of Poreplex & DeePlexiCon barcodes

DeePlexiCon of 20200605
```{r}
dir_bs <- "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/03.BarcodeProcessing/02.BarcodeSignalBinExp/20200605/"
files <- list.files(path = dir_bs, pattern = ".signal", full.names = TRUE)

Sigs0605 <- mclapply(FUN = function(x) {
  load(x)
  barcode
}, files, mc.cores = 4)
Sigs0605 <- do.call("c", Sigs0605)
```

Poreplex of 20200620
```{r}
dir_bs <- "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/03.BarcodeProcessing/02.BarcodeSignalBinExp/20200620/"
files <- list.files(path = dir_bs, pattern = ".signal", full.names = TRUE)

Sigs0620 <- mclapply(FUN = function(x) {
  load(x)
  barcode
}, files, mc.cores = 4)
Sigs0620 <- do.call("c", Sigs0620)
```

DeePlexiCon & Poreplex of 20200902
```{r}
dir_bs <- "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/03.BarcodeProcessing/02.BarcodeSignalBinExp/20200902/"
files <- list.files(path = dir_bs, pattern = ".signal", full.names = TRUE)

Sigs0902 <- mclapply(FUN = function(x) {
  load(x)
  barcode
}, files, mc.cores = 4)
Sigs0902 <- do.call("c", Sigs0902)
```

```{r}
Sigs0902 <- Sigs0902[names(Sigs0902) %in% read2gene_20200902$read]
```

DeePlexiCon & Poreplex of 20201127
```{r}
dir_bs <- "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/03.BarcodeProcessing/02.BarcodeSignalBinExp/20201127/"
files <- list.files(path = dir_bs, pattern = ".signal", full.names = TRUE)

Sigs1127 <- mclapply(FUN = function(x) {
  load(x)
  barcode
}, files, mc.cores = 4)
Sigs1127 <- do.call("c", Sigs1127)
```

```{r}
Sigs1127 <- Sigs1127[names(Sigs1127) %in% read2gene_20201127$read]
```

# Training set of DeePlexiCon & Poreplex

For DeePlexiCon software, we used 20200902 and 20201127 sequenced reads as training dataset to predict 20200605 sequenced reads.    

```{r}
DeePlexiCon_TrainingSet <- rbind(read2gene_20200902[grepl("^D-", Name), ], read2gene_20201127[grepl("^D-", Name), ])
```

```{r}
DeePlexiCon_TrainingSet_Signal <- c(Sigs0902[names(Sigs0902) %in% DeePlexiCon_TrainingSet$read], Sigs1127[names(Sigs1127) %in% DeePlexiCon_TrainingSet$read])
DeePlexiCon_TrainingSet <- DeePlexiCon_TrainingSet[read %in% names(DeePlexiCon_TrainingSet_Signal), ]
```

```{r}
DeePlexiCon_TrainingSet_Signal <- do.call(rbind, DeePlexiCon_TrainingSet_Signal)
colnames(DeePlexiCon_TrainingSet_Signal) <- paste0("BIN", sprintf("%03d", seq_len(ncol(DeePlexiCon_TrainingSet_Signal))))
```


For Poreplex software, we used 20200902 and 20201127 sequenced reads as training dataset to predict 20200620 sequenced reads.

```{r}
Poreplex_TrainingSet <- rbind(read2gene_20200902[grepl("^P-", Name), ], read2gene_20201127[grepl("^P-", Name), ])
```

```{r}
Poreplex_TrainingSet_Signal <- c(Sigs0902[names(Sigs0902) %in% Poreplex_TrainingSet$read], Sigs1127[names(Sigs1127) %in% Poreplex_TrainingSet$read])
Poreplex_TrainingSet <- Poreplex_TrainingSet[read %in% names(Poreplex_TrainingSet_Signal), ]
```

```{r}
Poreplex_TrainingSet_Signal <- do.call(rbind, Poreplex_TrainingSet_Signal)
colnames(Poreplex_TrainingSet_Signal) <- paste0("BIN", sprintf("%03d", seq_len(ncol(Poreplex_TrainingSet_Signal))))
```


# Test set of DeePlexiCon & Poreplex

```{r}
DeePlexiCon_TestSet <- read2gene_20200605
```

```{r}
DeePlexiCon_TestSet_Signal <- Sigs0605[names(Sigs0605) %in% DeePlexiCon_TestSet$read]
DeePlexiCon_TestSet <- DeePlexiCon_TestSet[read %in% names(DeePlexiCon_TestSet_Signal), ]
```

```{r}
DeePlexiCon_TestSet_Signal <- do.call(rbind, DeePlexiCon_TestSet_Signal)
colnames(DeePlexiCon_TestSet_Signal) <- paste0("BIN", sprintf("%03d", seq_len(ncol(DeePlexiCon_TestSet_Signal))))
```


```{r}
Poreplex_TestSet <- read2gene_20200620
```

```{r}
Poreplex_TestSet_Signal <- Sigs0620[names(Sigs0620) %in% Poreplex_TestSet$read]
Poreplex_TestSet <- Poreplex_TestSet[read %in% names(Poreplex_TestSet_Signal), ]
```

```{r}
Poreplex_TestSet_Signal <- do.call(rbind, Poreplex_TestSet_Signal)
colnames(Poreplex_TestSet_Signal) <- paste0("BIN", sprintf("%03d", seq_len(ncol(Poreplex_TestSet_Signal))))
```

# Save RData

DeePlexiCon_TrainingSet
```{r}
dim(DeePlexiCon_TrainingSet_Signal)
dim(DeePlexiCon_TrainingSet)
```

```{r}
setkey(DeePlexiCon_TrainingSet, read)
DeePlexiCon_TrainingSet[, Name := factor(Name)]
DeePlexiCon_TrainingSet_Signal <- DeePlexiCon_TrainingSet_Signal[DeePlexiCon_TrainingSet$read, ]
stopifnot(identical(row.names(DeePlexiCon_TrainingSet_Signal), DeePlexiCon_TrainingSet$read))
DeePlexiCon_TrainingSet_Signal <- as.data.frame(DeePlexiCon_TrainingSet_Signal)
```

```{r}
DeePlexiCon_TrainingSet_Signal$Class <- DeePlexiCon_TrainingSet$Name
```

```{r}
saveRDS(DeePlexiCon_TrainingSet_Signal, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/DeePlexiCon_TrainingSet.Rds")
```

```{r}
saveRDS(DeePlexiCon_TrainingSet, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/DeePlexiCon_TrainingSet_Meta.Rds")
```



DeePlexiCon_TestSet
```{r}
dim(DeePlexiCon_TestSet_Signal)
dim(DeePlexiCon_TestSet)
```

```{r}
setkey(DeePlexiCon_TestSet, read)
DeePlexiCon_TestSet[, Name := factor(Name)]
DeePlexiCon_TestSet_Signal <- DeePlexiCon_TestSet_Signal[DeePlexiCon_TestSet$read, ]
stopifnot(identical(row.names(DeePlexiCon_TestSet_Signal), DeePlexiCon_TestSet$read))
DeePlexiCon_TestSet_Signal <- as.data.frame(DeePlexiCon_TestSet_Signal)
```

```{r}
DeePlexiCon_TestSet_Signal$Class <- DeePlexiCon_TestSet$Name
```

```{r}
saveRDS(DeePlexiCon_TestSet_Signal, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/DeePlexiCon_TestSet.Rds")
```

```{r}
saveRDS(DeePlexiCon_TestSet, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/DeePlexiCon_TestSet_Meta.Rds")
```




Poreplex_TrainingSet
```{r}
dim(Poreplex_TrainingSet_Signal)
dim(Poreplex_TrainingSet)
```

```{r}
setkey(Poreplex_TrainingSet, read)
Poreplex_TrainingSet[, Name := factor(Name)]
Poreplex_TrainingSet_Signal <- Poreplex_TrainingSet_Signal[Poreplex_TrainingSet$read, ]
stopifnot(identical(row.names(Poreplex_TrainingSet_Signal), Poreplex_TrainingSet$read))
Poreplex_TrainingSet_Signal <- as.data.frame(Poreplex_TrainingSet_Signal)
```

```{r}
Poreplex_TrainingSet_Signal$Class <- Poreplex_TrainingSet$Name
```

```{r}
saveRDS(Poreplex_TrainingSet_Signal, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/Poreplex_TrainingSet.Rds")
```

```{r}
saveRDS(Poreplex_TrainingSet, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/Poreplex_TrainingSet_Meta.Rds")
```



Poreplex_TestSet
```{r}
dim(Poreplex_TestSet_Signal)
dim(Poreplex_TestSet)
```

```{r}
setkey(Poreplex_TestSet, read)
Poreplex_TestSet[, Name := factor(Name)]
Poreplex_TestSet_Signal <- Poreplex_TestSet_Signal[Poreplex_TestSet$read, ]
stopifnot(identical(row.names(Poreplex_TestSet_Signal), Poreplex_TestSet$read))
Poreplex_TestSet_Signal <- as.data.frame(Poreplex_TestSet_Signal)
```

```{r}
Poreplex_TestSet_Signal$Class <- Poreplex_TestSet$Name
```

```{r}
saveRDS(Poreplex_TestSet_Signal, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/Poreplex_TestSet.Rds")
```

```{r}
saveRDS(Poreplex_TestSet, 
        file = "/mnt/raid5/Personal/tangchao/project/Nanopore/BarcodeDecomplex/analysis/06.DecodingDeePlexiConAndPoreplex/00.ModelTraining/00.RData/Poreplex_TestSet_Meta.Rds")
```

